MergeBiomarkWith10X

### 2021-11-12 MergeBiomarkWith10X/MergeBiomarkWith10X.Rmd

# Setup
```{r setup, message=FALSE, warning=FALSE}
knitr::opts_knit$set(root.dir = "~/Desktop/10XGenomicsData/msAggr_scRNASeq/MergeBiomarkWith10X/")
library(dplyr)
library(Seurat)
library(patchwork)
library(ggplot2)
library(cowplot)
library(clustree)
```

## Set global variables
```{r}
pop.of.interest <- "CMP"
cellranger.folder <- "m2"
integrated.var <- 95
integrated.res <- ".0.5"
integrated.ident.list <- c("integrated_snn_res.0.5", "integrated_snn_res.1")
projectName <- paste0("MergeBiomarkWith10X_", pop.of.interest)
sc.pop.var <- 90
sc.pop.res <- ".0.5"
sc.ident.list <- c("RNA_snn_res.0.5", "RNA_snn_res.1")
```
source code
```{r}
source("~/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/metadata_overlap_stats.R")
source("~/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/ColorPalette.R")
source("~/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/PercentVariance.R")
source("~/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/read_10XGenomics_data.R")
source("~/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/Mouse2Human_idconversion.R")
```
store session info
```{r }
sink(paste0(projectName, "_sessionInfo.txt"))
sessionInfo()
sink()
```
# Create seurat objects

@@

```{r}
DimPlot(merged.object, reduction = "pca", group.by = "orig.ident")
```

@@

## load object
```{r}
tech.integrated <- readRDS(paste0(projectName, "_pctVar", integrated.var, ".RDS"))
tech.integrated <- SetIdent(tech.integrated, value = "integrated_snn_res.0.5")
tech.integrated@meta.data$orig.ident[tech.integrated@meta.data$orig.ident == paste0(pop.of.interest, cellranger.folder)] <- "10X"
tech.integrated@meta.data$orig.ident[tech.integrated@meta.data$orig.ident == paste0(pop.of.interest)] <- "biomark"
tech.integrated@meta.data$orig.ident <- factor(tech.integrated@meta.data$orig.ident)
```

@@

```{r}
fluor.cols <- names(mfi[, grepl("pos$", names(mfi))])
mfi.norm <- data.frame(matrix(nrow = 0, ncol = length(fluor.cols)))
colnames(mfi.norm) <- fluor.cols
for(sortdate in unique(mfi$sortdate)){
	mfi.subset <- scale(mfi[mfi$sortdate == sortdate, fluor.cols])
	mfi.norm <- rbind(mfi.norm, mfi.subset)
}
mfi.norm["pid"] <- do.call(rbind, strsplit(rownames(mfi.norm), '_'))[,3]
```
Add metadata column
```{r}
tech.integrated <- AddMetaData(tech.integrated, metadata = mfi.norm)
```
now plot some stuff
```{r}
biomark.integrated <- subset(tech.integrated, subset = orig.ident == "biomark")
```
```{r fig.height=12, fig.width=5}
RidgePlot(biomark.integrated, features = fluor.cols, cols = color.palette, ncol = 1)
```
```{r}
png(filename = paste0(projectName, "_pctVar", integrated.var, "res.", integrated.res, "-fluor.png"), height = 2400, width = 800)
RidgePlot(biomark.integrated, features = fluor.cols, cols = color.palette, ncol = 1)
dev.off()
```
plot umaps
```{r}
for(integrated.col in integrated.ident.list){
		plot.title <- paste0(projectName, "_pctVar", pct.var, "-mergedEnrichment_OrigIdent-Facet-integratedRes.", gsub("integrated_snn_res.", "", integrated.col))
		myplot <- DimPlot(tech.integrated, 
											group.by = "orig.ident",
											split.by = integrated.col, 
											reduction = "umap", 
											pt.size = 1.5,
											ncol = round(sqrt(length(levels(seurat.object@meta.data[[sc.col]])))),
											cols = color.palette) + 
			ggtitle(paste0(projectName, "_pctVar", pct.var, "-", integrated.col, " faceted by ", sc.col))
		plot(myplot)

@@

>>>>

# Setup
```{r setup, message=FALSE, warning=FALSE}
knitr::opts_knit$set(root.dir = "~/Desktop/10XGenomicsData/msAggr_scRNASeq/MergeBiomarkWith10X/")
library(dplyr)
library(Seurat)
library(patchwork)
library(ggplot2)
library(cowplot)
library(clustree)
# library(scatterplot3d)
library(rgl)
```

## Set global variables
```{r}
pop.of.interest <- "CMP"
cellranger.folder <- "m2"
integrated.var <- 95
integrated.res <- ".1"
integrated.ident.list <- c("integrated_snn_res.0.5", "integrated_snn_res.1", "integrated_snn_res.1.5")
projectName <- paste0("MergeBiomarkWith10X_", pop.of.interest)
sc.pop.var <- 90
sc.pop.res <- ".0.5"
sc.ident.list <- c("RNA_snn_res.0.5", "RNA_snn_res.1")
```
source code
```{r}
source("~/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/metadata_overlap_stats.R")
source("~/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/ColorPalette.R")
source("~/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/PercentVariance.R")
source("~/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/read_10XGenomics_data.R")
source("~/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/Mouse2Human_idconversion.R")
```
store session info
```{r }
sink(paste0(projectName, "_sessionInfo.txt"))
sessionInfo()
sink()
```
# Create seurat objects

@@

```{r}
DimPlot(merged.object, reduction = "pca", group.by = "orig.ident", cols = c("black", "red"), pt.size = 1)
png(filename = paste0(projectName, "merged_PCA.png"), height = 800, width = 800)
DimPlot(merged.object, reduction = "pca", group.by = "orig.ident", cols = c("black", "red"), pt.size = 2)
dev.off()
```

@@

## load object
```{r}
tech.integrated <- readRDS(paste0(projectName, "_pctVar", integrated.var, ".RDS"))
tech.integrated <- SetIdent(tech.integrated, value = paste0("integrated_snn_res", integrated.res))
tech.integrated@meta.data$orig.ident[tech.integrated@meta.data$orig.ident == paste0(pop.of.interest, cellranger.folder)] <- "10X"
tech.integrated@meta.data$orig.ident[tech.integrated@meta.data$orig.ident == paste0(pop.of.interest)] <- "biomark"
tech.integrated@meta.data$orig.ident <- factor(tech.integrated@meta.data$orig.ident)
```

@@

```{r}
fluor.cols <- names(mfi[, grepl("pos$", names(mfi))])
mfi.norm <- data.frame(matrix(nrow = 0, ncol = length(fluor.cols)))
colnames(mfi.norm) <- fluor.cols
for(sortdate in unique(mfi$sortdate)){
	mfi.subset <- scale(mfi[mfi$sortdate == sortdate, fluor.cols])
	mfi.norm <- rbind(mfi.norm, mfi.subset)
}
mfi.norm["pid"] <- do.call(rbind, strsplit(rownames(mfi.norm), '_'))[,3]
```
Add metadata column
```{r}
tech.integrated <- AddMetaData(tech.integrated, metadata = mfi.norm)
```
now plot some stuff
```{r}
biomark.integrated <- subset(tech.integrated, subset = orig.ident == "biomark")
```
```{r fig.height=12, fig.width=5}
RidgePlot(biomark.integrated, features = fluor.cols, cols = color.palette, ncol = 1)
```
```{r}
png(filename = paste0(projectName, "_pctVar", integrated.var, "res", integrated.res, "-fluor.png"), height = 2400, width = 800)
RidgePlot(biomark.integrated, features = fluor.cols, cols = color.palette, ncol = 1)
dev.off()
```
plot umaps
```{r}
for(integrated.col in integrated.ident.list){
		plot.title <- paste0(projectName, "_pctVar", pct.var, "-mergedEnrichment_OrigIdent-Facet-integratedRes.", gsub("integrated_snn_res.", "", integrated.col))
		myplot <- DimPlot(tech.integrated, 
											group.by = "orig.ident",
											split.by = integrated.col, 
											reduction = "umap", 
											pt.size = 1.5,
											ncol = round(sqrt(length(levels(tech.integrated@meta.data[[sc.col]])))),
											cols = color.palette) + 
			ggtitle(paste0(projectName, "_pctVar", pct.var, "-", integrated.col, " faceted by ", sc.col))
		plot(myplot)

@@

# Plot 3D
Plot in 3d
```{r}
tot.var <- percent.variance(tech.integrated@reductions$pca@stdev, plot.var = FALSE, return.val = TRUE)
ndims <- length(which(cumsum(tot.var) <= integrated.var))
tech.integrated.3d <- tech.integrated
tech.integrated.3d <- FindNeighbors(tech.integrated.3d, dims = 1:ndims)
tech.integrated.3d <- FindClusters(tech.integrated.3d, resolution = as.numeric(integrated.res))
tech.integrated.3d <- RunUMAP(tech.integrated.3d, dims = 1: ndims, n.components = 3)
```
Plot 3D UMAP

```{r}
tech.integrated.3d <- SetIdent(tech.integrated.3d, value = paste0("integrated_snn_res", integrated.res))
my_object <- tech.integrated.3d@reductions$umap@cell.embeddings

# color.palette @ res.0.5 has 15 levels. Change color.palette[11] to a different color so can add the biomark cells as large black dots afterwards
color.palette[11] <- "mediumpurple1"
par3d("windowRect" = c(122, 44, 950, 929))
plot3d(x=my_object[,1], y=my_object[,2], z=my_object[,3], 
			 col = color.palette[tech.integrated.3d@active.ident], 
			 box=FALSE, axes=FALSE, xlab = "", ylab = "", zlab = "")
rgl.lines(c(-10, 10), c(0, 0), c(0, 0), color = "black")
rgl.lines(c(0, 0), c(-10, 10), c(0, 0), color = "red")
rgl.lines(c(0, 0), c(0, 0), c(-10, 10), color = "green")

biomark.embeddings <- subset(tech.integrated.3d, subset = orig.ident == "biomark")
biomark.embeddings <- biomark.embeddings@reductions$umap@cell.embeddings
plot3d(x = biomark.embeddings[,1], y = biomark.embeddings[,2], z = biomark.embeddings[,3],
			 col = "black", size = 10,
			 add = TRUE)
rgl.viewpoint(zoom = .5)
movie3d(spin3d(axis = c(1, 1, 1), rpm = 6), duration = 10, dir = getwd(), clean = TRUE, webshot = TRUE, movie = "MergeBiomarkWith10X_CMP_pctVar95res.1.5")
```

# Find Seurat v1 cells
## Add cluster IDs from Seurat v1
Exported cell IDs for clusters 3, 17, 10, 11 from Seurat v1. Will add these IDs as a metadata column.  
Create column "clust.ID" and populate with 0's. Then import IDs for clusters
```{r}
clust3.cells <- read.table(file = "/Users/heustonef/Desktop/10XGenomicsData/msAggr_scRNASeq/Seuratv1_clusterCellIDs/cluster3cellIDs.txt", col.names = "clust03")
clust3.cells <- sapply(clust3.cells, function(x) paste0(gsub("CMP", "CMPm2", x), "-1"))
clust17.cells <- read.table(file = "/Users/heustonef/Desktop/10XGenomicsData/msAggr_scRNASeq/Seuratv1_clusterCellIDs/cluster17cellIDs.txt", col.names = "clust17")
clust17.cells <- sapply(clust17.cells, function(x) paste0(gsub("CMP", "CMPm2", x), "-1"))
clust10.cells <- read.table(file = "/Users/heustonef/Desktop/10XGenomicsData/msAggr_scRNASeq/Seuratv1_clusterCellIDs/cluster10cellIDs.txt", col.names = "clust10")
clust10.cells <- sapply(clust10.cells, function(x) paste0(gsub("CMP", "CMPm2", x), "-1"))
clust11.cells <- read.table(file = "/Users/heustonef/Desktop/10XGenomicsData/msAggr_scRNASeq/Seuratv1_clusterCellIDs/cluster11cellIDs.txt", col.names = "clust11")
clust11.cells <- sapply(clust11.cells, function(x) paste0(gsub("CMP", "CMPm2", x), "-1"))
```

## map cluster ids from Seuratv1
```{r}
seurat.object@meta.data$clust.ID[rownames(seurat.object@meta.data) %in% clust3.cells] <- 3
seurat.object@meta.data$clust.ID[rownames(seurat.object@meta.data) %in% clust17.cells] <- 17
seurat.object@meta.data$clust.ID[rownames(seurat.object@meta.data) %in% clust10.cells] <- 10
seurat.object@meta.data$clust.ID[rownames(seurat.object@meta.data) %in% clust11.cells] <- 11
seurat.object@meta.data[is.na(seurat.object@meta.data)] <- 0
seurat.object@meta.data$clust.ID <- as.factor(seurat.object@meta.data$clust.ID)
```
## plot something
```{r}
DimPlot(tech.integrated, group.by = "clust.ID", split.by = "integrated_snn_res.1.5", cols = c("black", "green", "blue", "red", "orange"), ncol = 4)
```

```{r}
test.col.pattern <- "RNA_snn_res.1"
target.col.pattern <- "integrated_snn_res"
xlsx_filename <- paste0(projectName, "_pctVar", pct.var, "_mergedEnrichmentStats_Sv4B.xlsx")

metadata_overlap_stats(seurat.object = seurat.object, 
											 target.col.pattern = target.col.pattern, 
											 test.col.pattern = test.col.pattern, 
											 print_to_screen = TRUE,
											 xlsx_filename = xlsx_filename)

## map cluster ids from Seuratv1
```{r}
tech.integrated@meta.data$clust.ID[rownames(tech.integrated@meta.data) %in% clust3.cells] <- 3
tech.integrated@meta.data$clust.ID[rownames(tech.integrated@meta.data) %in% clust17.cells] <- 17
tech.integrated@meta.data$clust.ID[rownames(tech.integrated@meta.data) %in% clust10.cells] <- 10
tech.integrated@meta.data$clust.ID[rownames(tech.integrated@meta.data) %in% clust11.cells] <- 11
tech.integrated@meta.data[is.na(tech.integrated@meta.data)] <- 0
tech.integrated@meta.data$clust.ID <- as.factor(tech.integrated@meta.data$clust.ID)
```
## plot something
```{r}
DimPlot(tech.integrated, group.by = "clust.ID", split.by = "integrated_snn_res.1.5", cols = c("black", "green", "blue", "red", "orange"), ncol = 11)
```

```{r}
DimPlot(seurat.object, group.by = "clust.ID", cols = c("black", "green", "blue", "red", "orange"))
DimPlot(seurat.object, group.by = "clust.ID", split.by = "RNA_snn_res.1", cols = c("black", "green", "blue", "red", "orange"), ncol = 5)

png(filename = paste0(projectName, "_pctVar", pct.var, "-Sv1ClustID_on_Sv4.png"), height = 800, width = 800)
DimPlot(seurat.object, group.by = "clust.ID", cols = c("black", "green", "blue", "red", "orange"), pt.size = 1)
dev.off()
png(filename = paste0(projectName, "_pctVar", pct.var, "-Sv1ClustID_on_Sv4-facetSv4.png"), height = 800, width = 800)
DimPlot(seurat.object, group.by = "clust.ID", split.by = "RNA_snn_res.1", cols = c("black", "green", "blue", "red", "orange"), ncol = 5) + NoAxes() + NoLegend()
dev.off()
```

## generate emphasis colorpalette
```{r}
emphasis.palette <- rep("black", times = 25)
```

```{r}
emphasis.palette.Sv4 <- emphasis.palette
emphasis.palette.Sv4[c(4, 6, 7, 8)] <- c("green", "orange", "red", "blue")
DimPlot(seurat.object, group.by = "RNA_snn_res.1", split.by = "integrated_snn_res.1.5", cols = emphasis.palette.Sv4, ncol = 5)

png(filename = paste0(projectName, "_pctVar", pct.var, "-Sv4ClustID_on_Sv4B-facetSv4B.png"), height = 800, width = 800)
DimPlot(seurat.object, group.by = "RNA_snn_res.1", split.by = "integrated_snn_res.1.5", cols = emphasis.palette.Sv4, ncol = 5) + NoAxes()
dev.off()
```
